Different Cost

### 2022-10-20 graphs_newt_snakes/dif_cost.Rmd
Looked at more data and added maps to my slim script! Need to fix corcompare to look nicer and spend a lot of time writing about all of these new results.

trends_by_gen(GA1_lit_cost_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 50000, rep=0)

>>>>

trends_by_gen(GA1_lit_cost_file, title="Space Tall: Newt VS Snake Population Size GA1", subt="Gen 16sims", y_label="Mean Phenotype", x_label="Generations", 100, 30000, rep=0)
